### 2015-07-14 thesis/thesis/chap6/chap6.tex
changes

In this theses we proposed three models for aggregation of web services within communities. The goal of our models are to maximize efficiency by collaborating and forming stable communities. In our first contributions we focused on stability and fairness for all web services within the communities. In this work we addressed the shortcomings of community formation in recent work such as considering best strategies which benefit all services involved, making solutions practical in real-time settings and also fairness and stability of communities. The proposed model offers an applicable mechanism for membership requests and selection of web services. The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more tasks with high quality.

In our next step of research work, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and membership management in communities of web services. In this work we tried to tackle the issue of autonomous web services not having a centralized architecture and complete information of all the parameters of other web services. The proposed mechanism helps web services and communities decide with whom to be grouped and cooperate. DDM first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Communities and web services can use the trained model and instantly choose best-response strategies considering their long-term gain. In fact, the decision making mechanism is implemented as a decision tree of possible viable strategies along with their long-term expected utility. The ultimate goal of our mechanism is to choose the best decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature. The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions. The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.

In our final step of the work, the focus was on inter-community interaction between services involved within the community. The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behaviour of intelligent services that are active within communities. We considered two acting strategies where service agenets expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers. Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes. The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities. The theoretical results presented in this thesis are also backed by simulation results using a real services dataset. Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
services deviate from the coopetitive strategy suggested by our decision-making mechanism the more they make less benefits. Thus, deviating from our coopetitive strategy yields less income for the service.

>>>>

In this theses we proposed three models for aggregation of web services within communities. The goal of our models are to maximize efficiency by collaborating and forming stable communities. In our first contributions we focused on stability and fairness for all web services within the communities. In this work we addressed the shortcomings of community formation in recent work such as considering best strategies which benefit all services involved, making solutions practical in real-time settings and also fairness and stability of communities. The proposed model offers an applicable mechanism for membership requests and selection of web services. The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more tasks with high quality. The theoretical and extensive simulation results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-optimal decision making mechanisms.

In our next step of research work, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and membership management in communities of web services. In this work we tried to tackle the issue of autonomous web services not having a centralized architecture and complete information of all the parameters of other web services. The proposed mechanism helps web services and communities decide with whom to be grouped and cooperate. DDM first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Communities and web services can use the trained model and instantly choose best-response strategies considering their long-term gain. In fact, the decision making mechanism is implemented as a decision tree of possible viable strategies along with their long-term expected utility. The ultimate goal of our mechanism is to choose the best decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature. We performed excrements using real date from 142 users on 4,532 web services during 64 different time slots. The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions. Moreover, the experiments using real data samples support the need for a long-term training model in a successful decision making process.

In our final step of the work, the focus was on inter-community interaction between services involved within the community. The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behaviour of intelligent services that are active within communities. We considered two acting strategies where service agenets expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers. Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes. The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities. The theoretical results presented in this thesis are also backed by simulation results using a real services dataset. Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real services dataset on the web. Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
services deviate from the coopetitive strategy suggested by our decision-making mechanism the more they make less benefits.
